### 2023-09-21 doc/15yrsChange.Rmd
@llmorreale will be lead author
update list of figures & hypotheses based on group discussion

#Figures
photos = 1
photo_represenative_upland = "1a"
photo_deer_exclosure = "1b"
photo_graveyard = "1c"
```

@@

Here, we use 15 years of detailed census data from a large forest dynamics plot including a 4-ha deer exclosure to test the following hypotheses:
(1) canopy tree mortality and associated biomass loss are increasing, in large part due to non-endemic nuisance species (pests & pathogens)
(2) growth and recruitment (outside deer exclosure) have not kept pace with tree mortality, resulting in declining AGB (-∆AGB)
(3) C stocks have declined (-∆AGB), and will decline further if current trends continue

@@

![**Photos within the SCBI ForestGEO plot: (a) represenative upland forest, (b) deer exclosure, (c) "tree graveyard" in NE corner ** *(Perhaps combine these with a map of the plot?)*](display/photos.png)

>>>>

#Figures
map_and_photos = 1
photo_represenative_upland = "1a"
photo_deer_exclosure = "1b"
photo_graveyard = "1c"

biomass_trends = 2 #line plot showing biomass through time for entire plot and each of the 3 focal sections

loss_gain_net = 3 # 4-panel figure showing ∆AGB, loss, and gain for (a) whole plot, (b) upland, (c) deer exclosure, (d) graveyard

mortality_by_genera = 4 # 4-panel figure showing biomass mortality by genera for for (a) whole plot, (b) upland, (c) deer exclosure, (d) graveyard

regen_failure = 5 #some figure illustrating absence of small canopy trees/ shifting  size distributions

```

@@

Here, we use 15 years of detailed census data from a large forest dynamics plot including a 4-ha deer exclosure to test the following hypotheses:
(1) C stocks have declined (-∆AGB)
(2) canopy tree mortality and associated biomass loss are increasing, in large part due to non-endemic nuisance species (pests & pathogens)
(3) recruitment (outside deer exclosure) and growth have not kept pace with tree mortality, implying that future mortality will result in substantial net biomass loss (regeneration debt)

@@

![**Figure `r map_and_photos`. Photos within the SCBI ForestGEO plot: (a) represenative upland forest, (b) deer exclosure, (c) "tree graveyard" in NE corner ** *(Perhaps combine these with a map of the plot?)*](display/photos.png)
